Exploitation Techniques and Mitigations

### 2016-01-26 docs/paper.tex
Paper: Draft conclusion

>>>>

String with no mitigation mechanisms in place, we have seen how easy it is to
manipulate the program by exploiting just one simple buffer overflow. Going
beyond simple manipulations like changing locale variables, we craft shell code
and injected it to open up a shell accepting and executing arbitrary inputs.
Next, Data Execution Prevention (DEP) was presented to deny the ability of
\emph{injecting} new code.

This was countered by introducing Return Oriented Programming (DEP) (and
ret2libc) which removes the requirement of injecting new code to exploit a
binary. This is done by combining code fragments (gadgets) already available in
the target binary and libraries to build new, malicious sequences of
instructions.

Address Space Layout Randomization (ASLR) can be defeated with an information
leak and even the StackGuard mechanism can broking with brute force (including
an unexpected low upper bound) in certain scenarios.

The basic idea behind Control-Flow Integrity (CFI) was communicated after this
followed by a small glance at \texttt{printf}'s capabilities to work as an
interpreter. Along the way references have been provided to aid the reader.

Before concluding with this section a short word about other architectures and
their influence on these techniques has been given,

Happy Hacking
